\textmd{\hmwkClass:\ \hmwkTitle}\\ \\ \small{Due\ on\ \hmwkDueDate}

### 2017-05-07 paper/main.tex
more details

\section{What we did}

\section{How we did it}

\section{Why we did it this way}

\section{Demos}

>>>>

\section{Infrastructure}
generic procedures, ps4 stuff
what we did, how we did it, why we did it

\section{Arithmetic}
vector arithmetic
what we did, how we did it, why we did it

\section{Physics Engine}
each object does its own updating, procedures are objects
what we did, how we did it, why we did it

\section{Demos}
binary stars, solar system, magnetics, magnetic solar system
